
%=== File containing Global Configuration of the report ===%
%                                                          %
% Copyright (C) ISI - All Rights Reserved                  %
% Proprietary                                              %
% Written by Med Hossam <med.hossam@gmail.com>, April 2016 %
%                                                          %
% @author: HEDHILI Med Houssemeddine                       %
% @linkedin: http://tn.linkedin.com/in/medhossam           %
%==========================================================%

%=========== You MUST type your information here ==========%
% global_config.tex file is designed to configure your     %
% cover pages (main, back and black covers)                %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Mise en place d'un pipeline CI/CD pour un serveur Asterisk avec l'automatisation de l’approvisionnement via Terraform sur AWS}

\author{Wiem FEDDAOUI}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{Diplôme National d’Ingénieur en Sciences Appliquées et Technologies}
\speciality{Ingénierie et Développement des Infrastructures
et des \\ Services de Communications}
%\speciality{Génie des Télécommunications et Réseaux}
%\speciality{Génie Informatique des Systèmes Industriels}

%% Encadrant professionnel
\proFramerName{Monsieur Mohammed TLICH }


%% Encadrant académique
\academicFramerName{Madame Meha HACHANI}

%% Entreprise d'accueil
\companyName{Luceor Labs}

%% Année universitaire
\collegeYear{2023 - 2024}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{J'autorise l'étudiante à faire le dépôt de son rapport de stage en vue d'une soutenance.}

\academicSignSentence{J'autorise l'étudiante à faire le dépôt de son rapport de stage en vue d'une soutenance.}

%%% AR

\arabicAbstract{
الهدف الرئيسي من هذا العمل النهائي هو أتمتة بنية تحتية سحابية باستخدام تيرافورم وتطبيق نهج التطوير والعمليات مع التكامل المستمر والنشر المستمر لنظام أستريسك. هدفت هذه الخطوة إلى جعل عملية التطوير سلسة وفعالة من خلال أتمتة بناء صور دوكر لنظام أستريسك، والنشر على البنية التحتية السحابية التي تم إنشاؤها، وكذلك استخدام منصة جيت هاب لإدارة الشيفرة المصدرية.
}

\arabicAbstractKeywords{التطوير والعمليات، التكامل المستمر والنشر المستمر، نظام أستريسك، منصة جيت هاب/إجراءات جيت هاب، تيرافورم، خدمات أمازون السحابية}



%% To use latin characters inside the arabic text
% just put them inside the command \textLR{}
%%%%

%%% FR
\frenchAbstract{
L'objectif principal de ce travail de fin d'études est d'automatiser une infrastructure cloud à l'aide de Terraform et de mettre en place une approche DevOps avec intégration continue et déploiement continu (CI/CD) pour le système Asterisk. Cette démarche visait à rendre le processus de développement fluide et efficace, en automatisant la construction des images Docker Asterisk, le déploiement sur l'infrastructure cloud créée, ainsi que l'utilisation de GitHub pour la gestion du code source.
}

\frenchAbstractKeywords{DevOps CI/CD, Asterisk, GitHub/GitHub Actions, Terraform, AWS}

%%% EN
\englishAbstract{
The main objective of this end-of-studies project is to automate a cloud infrastructure using Terraform and implement a DevOps approach with continuous integration and continuous deployment (CI/CD) for the Asterisk system. This approach aimed to make the development process smooth and efficient by automating the building of Docker Asterisk images, deployment on the created cloud infrastructure, and using GitHub for source code management.
}

\englishAbstractKeywords{DevOps CI/CD, Asterisk, GitHub/GitHub Actions, Terraform, AWS}

%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
